\chapter{Sponsorships and thanks}
We cannot thank enough the following organisations who have supported the Migovec expeditions over the years, and in particular from 2013 to 2017.
\begin{citemize}
\item The \textsc{Ghar Parau Foundation} for  the \textsc{Ghar Parau Expedition Grant Award}, its subset, the \textsc{Alex Pitcher Award} which helped new young cavers buy their caving helmets and lights and allowed them into expedition caving. This ongoing support played a pivotal role in promoting a thriving club community.

\item The \textsc{Imperial College Trust} for Tours funding for the financial support directed at transportation subsidy.
\item The \textsc{Harlington Trust} for the substantial financial support in acquiring new SRT equipment (Februabry 2014, March 2015) and 3 Cave-Link radios sets (July 2017).
\item \textsc{UK Caving} for the award of 300m of Spanset Rope in 2017, used  in part for the rigging of Galaktika, the largest chamber in the System. (more information at \emph{https://ukcaving.com/board/})
\item The \textsc{2012} and \textsc{2016 Viljem Putick Prize} awarded for best Slovenian exploration project, put to good use in the purchase of additional rigging equipment.
\item \textsc{Felix}, the Imperial College weekly newspaper for the publication of exploration stories
\item \textsc{Imperial Reporter}
\item The \textsc{Imperial College Exploration Board}.

\mydelimiter

\item All photographers, authors, cartoonists who contributed to this project, for their work, advice and encouragement as this book took shape. Particularly to \emph{Jack Hare}, \emph{Rhys Tyers} and \emph{Alexander Seaton} whose input was invaluable. 

\item \emph{Tony Seddon} for the annual rescue practice sessions held in the UK, general advice and equipment supplies.

\item \emph{Mark} and \emph{Jim Evans}, for starting it all for ICCC, and for coming back often to share stories of early exploration at the sunset spot.
\item The \emph{old lags}, for want of a better name, who come back to Slovenia year after year to teach the ways of Mig to young people thirsty for adventure, why are you so good at crosswords?
\item \emph{James 'Tetley' Hooper}, thanks for letting us use your flat as a base for so many years. It would not have been the same without you.
\item \emph{Janet Cotter}, for doing a million tasks in the Bivi and always cracking a smile for returning hungry cavers. 
\item \emph{Jarvist Frost} for the colossal amount of work dedicated to the Hollow Mountain project, which is very much the inspiration and basis for this book. 
\item \emph{Dave Wilson}, for the technical expertise in setting up the solar panel electronics, on which the expedition depends.

\item The \emph{Klobu\v{c}ar} family: Slavica, Marjan, Nada, Zoran... for the generous use of the barn to store equipment and park the van during the expeditions. The farewell curd-cheese cakes and lemon infused \v{z}ganje will not be forgotten.

\item Our friends at the JSPDT, with whom we've shared the toil and the rewards under Migovec.
\item The \textsc{Jamarska Re\v{s}evalna Slu\v{z}ba} (JRS), the \textsc{Jamarska zveza Slovenije} (JZS) whithin which it operates, the helicopter pilot from mountain rescue services whom we must thank again, and to whom we owe the successful recovery of Arun Paul.
\item \emph{Zdenko Rejec}, for letting us into Primadona's secrets. We will keep going left, into the blank mountain.
\item \emph{Jana \v{C}arga} for the work behind the scenes at the helm of the JSPDT, for organising the permits, memberships and inviting us again and again to Tolmin.
\item \emph{Andrej Fratnik}, whose welcoming spirit sparked this joint venture and whose participation in the project from the very early start to this day has never faltered. 
\end{citemize}
