\section{Sponsorships and thanks}
We cannot thank enough the following organisations who have supported the Migovec expeditions over the years, and in particular from 2013 to 2017.
\begin{citemize}
\item The Ghar Parau foundation for financial support, its subset, the Alex Pitcher awards which helped new cavers buy their caving helmets and lights.
\item The Imperial College Union for Tour funding for the financial support directed at transportation subsidy.
\item The Harlington Trust for the financial support in acquiring 3 Cave-Link radios sets in 2017, and contribution.
\item Uk Caving for the award of 300m of Spanset Rope in 2017, used for the rigging to Galaktika, the largest chamber in the System.
\item The Putick Prize awarded in 2013 and 2017 for best Slovenian exploration project, put to good use in the purchase of additional rigging equipment.
\item Felix, the Imperial College weekly newspaper for the publication of exploration stories
\item The Imperial College Exploration Board. 


\item All photographers, authors, cartoonists who contributed to this project, for their work, advice and encouragement as this book took shape. Particularly to Jack Hare, Rhys Tyers and Alexander Seaton whose input was invaluable. 

\item Tony Seddon for the annual rescue practice sessions held in the UK, general advice and equipment supplies.

\item Mark and Jim Evans, for starting it all for ICCC, and for coming back often to share stories of early exploration at the sunset spot.
\item The old lags (for want of a better name), who come back to Slovenia year after year to teach the ways of Mig to young people thirsty for adventure, why are you so good at crosswords?
\item James 'Tetley' Hooper, for the offer to use the Tolmin flat as a base in early expeditions and the 
\item Janet Cotter, for doing a million tasks in the Bivi and always cracking a smile for returning hungry cavers. 
\item Jarvist Frost for the colossal amount of work dedicated to the Hollow Mountain project, which is very much the inspiration and basis for this book. 
\item Dave Wilson, for the technical expertise in setting up the solar panel electronics, on which the expedition depends.

\item The Koblu\v{c}ar family, Slavica, Marjan, Nada, Zoran... for the generous use of the barn to store equipment and park the van during the expeditions. The farewell curd cheesecakes and lemon infused \v{z}ganje will not be forgotten.

\item Our friends at the JSPDT, with whom we've shared the toil and the rewards under Migovec.
\item Zdenko, for letting us into Primadona's secrets. We will keep going left, into the blank mountain.
\item Jana \v{C}arga for the work behind the scenes at the helm of the JSPDT, for organising the permits, memberships and inviting us again and again. 
\item Andrej Fratnik
\end{citemize}
